MINOS Handover Plots

### 2024-01-15 minos/validation/cross_validation_default.Rmd

## Job Sec

```{r}
jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'job_sec')

cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
                 var = 'job_sec',
                 save = FALSE)
rm(jobsec.pivoted)
```

## Hourly Wage

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
multi_year_boxplots(raw, cv, 'hourly_wage')
q_q_comparison(raw, cv, 'hourly_wage')
```

## Children Ageing

@@

>>>>

## CHILDREN AGEING

@@

# CHILD POVERTY VARS

## Relative Poverty

```{r}
relative_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                   df1.name = 'simulated', 
                                                   df2 = raw, 
                                                   df2.name = 'raw', 
                                                   var = 'relative_poverty')

cv_ordinal_plots(pivoted.df = relative_poverty.pivoted, 
                 var = 'relative_poverty',
                 save = FALSE)
rm(relative_poverty.pivoted)
```

## Absolute Poverty

```{r}
absolute_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                   df1.name = 'simulated', 
                                                   df2 = raw, 
                                                   df2.name = 'raw', 
                                                   var = 'absolute_poverty')

cv_ordinal_plots(pivoted.df = absolute_poverty.pivoted, 
                 var = 'absolute_poverty',
                 save = FALSE)
rm(absolute_poverty.pivoted)
```

## Material Deprivation

```{r}
matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
                                               df1.name = 'simulated', 
                                               df2 = raw, 
                                               df2.name = 'raw', 
                                               var = 'matdep_child')

cv_ordinal_plots(pivoted.df = matdep_child.pivoted, 
                 var = 'matdep_child',
                 save = FALSE)
rm(matdep_child.pivoted)
```

## Low Income and Material Deprivation

```{r}
low_income_matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                          df1.name = 'simulated', 
                                                          df2 = raw, 
                                                          df2.name = 'raw', 
                                                          var = 'low_income_matdep_child')

cv_ordinal_plots(pivoted.df = low_income_matdep_child.pivoted, 
                 var = 'low_income_matdep_child',
                 save = FALSE)
rm(low_income_matdep_child.pivoted)
```

## Persistent Poverty

```{r}
persistent_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                     df1.name = 'simulated', 
                                                     df2 = raw, 
                                                     df2.name = 'raw', 
                                                     var = 'persistent_poverty')

cv_ordinal_plots(pivoted.df = persistent_poverty.pivoted, 
                 var = 'persistent_poverty',
                 save = FALSE)
rm(persistent_poverty.pivoted)
```

### 2024-01-15 minos/validation/handovers.Rmd

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
# out.path <- here::here('output', 'child_poverty_config/')
# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
```

@@

@@

```{r}

>>>>

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

#out.path <- here::here('output', 'scotland_scaled/')
#base.dat <- read_first_singular_local_out(out.path, '25UniversalCredit', drop.dead = TRUE)

# HR 283-285 older version (285)
# out.path <- here::here('output', 'child_poverty_config/')
# base.dat <- read_singular_local_out(out.path, 'ChildPovertyIntervention', drop.dead = TRUE)
```

@@

## Child Ages

```{r}
base.child.ages <- base.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2009) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

s<- strsplit(base.child.ages$child_ages, "_")

base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
base.child.ages.expanded <- base.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n())

ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

base.child.ages.nkids <- base.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts))

ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
  geom_line() +
  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

@@
